Bird beak's elaboration and innovation

### 2022-06-16 Analysis/10-sensitivity_analysis.Rmd
Update 10-sensitivity_analysis.Rmd

## Original, BM space and randomised spaces (same parameters)

@@

@@

Model       | parameters      | replicates | trees sampled | spaces sampled | posterior VCVs |
------------|-----------------|------------|---------------|----------------|----------------|
shapespace  | from shapespace | 100        | 100           | 1              | 1000 |
randomspace | from shapespace | 100        | 100           | 25             | 1000 |
BMspace     | from shapespace | 100        | 100           | 25             | 1000 |
ballspace   | from ballspace  | 100        | 100           | 1              | 1000 |

@@

>>>>

## Original and randomised spaces (same parameters)

@@

## BM space

For the BM space, the parameters are estimated for each simulation individually to avoid corner case bugs (e.g. wrong Choleski decompositions!).
We used three chains of 20000 iterations for the parameterisation chains.

@@

Model       | parameters      | replicates | trees sampled | spaces sampled | posterior VCVs |
------------|-----------------|------------|---------------|----------------|----------------|
shapespace  | from shapespace | 100        | 100           | 1              | 1000 |
randomspace | from shapespace | 100        | 100           | 25             | 1000 |
BMspace     | from each BMspace | 100        | 100           | 25             | 1000 |
ballspace   | from ballspace  | 100        | 100           | 1              | 1000 |

## Combining and diagnosing the results

```{r, eval = TRUE, echo = FALSE}
## Set up the variables
models_path <- "../Data/Cluster/shapespace_charadriiformes/"
model_files <- list.files(models_path, pattern = ".rda")

## Original space
shapespace_models_names <- model_files[grep("shapespace", model_files)]
## Models placeholder
shapespace_models <- list()

## Load the models
for(i in 1:length(shapespace_models_names)) {
      load(paste0(models_path, shapespace_models_names[i], collapse = "/"))
      shapespace_models <- c(shapespace_models, shapespace_20)
}

## Combine and diagnose
shapespace_charadriiformes_posteriors <- combine.mini.chains(shapespace_models)
silent <- diagnose.mini.chains(shapespace_charadriiformes_posteriors)
save(shapespace_charadriiformes_posteriors, file = "../Data/Processed/shapespace_charadriiformes_posteriors.MCMCglmm")

```

Figure 6: Original shapespace mcmcmcglmmm diagnosis

```{r, eval = TRUE, echo = FALSE}
## Ball space
ballspace_models_names <- model_files[grep("ballspace", model_files)]
## Models placeholder
ballspace_models <- list()

## Load the models
for(i in 1:length(ballspace_models_names)) {
      load(paste0(models_path, ballspace_models_names[i], collapse = "/"))
      ballspace_models <- c(ballspace_models, ballspace_20)
}

## Combine and diagnose
ballspace_charadriiformes_posteriors <- combine.mini.chains(ballspace_models)
silent <- diagnose.mini.chains(ballspace_charadriiformes_posteriors)
save(ballspace_charadriiformes_posteriors, file = "../Data/Processed/ballspace_charadriiformes_posteriors.MCMCglmm")
```

Figure 7: Balled shapespace mcmcmcglmmm diagnosis

```{r, eval = TRUE, echo = FALSE}
## Random space
randospace_models_names <- model_files[grep("randospace", model_files)]
## Models placeholder
randospace_models <- list()

## Load the models
for(i in 1:length(randospace_models_names)) {
      load(paste0(models_path, randospace_models_names[i], collapse = "/"))
      randospace_models <- c(randospace_models, unlist(randospace_20, recursive = FALSE))
}

## Combine and diagnose
randospace_charadriiformes_posteriors <- combine.mini.chains(randospace_models)
silent <- diagnose.mini.chains(randospace_charadriiformes_posteriors)
save(randospace_charadriiformes_posteriors, file = "../Data/Processed/randospace_charadriiformes_posteriors.MCMCglmm")
```

Figure 8: Randomised shapespace mcmcmcglmmm diagnosis

```{r, eval = FALSE, echo = FALSE}
## Random space
BMspace_models_names <- model_files[grep("BMspace", model_files)]
## Models placeholder
BMspace_models <- list()

## Load the models
for(i in 1:length(BMspace_models_names)) {
      load(paste0(models_path, BMspace_models_names[i], collapse = "/"))
      BMspace_models <- c(BMspace_models, unlist(BMspace_20, recursive = FALSE))
}

## Combine and diagnose
BMspace_charadriiformes_posteriors <- combine.mini.chains(BMspace_models)
silent <- diagnose.mini.chains(BMspace_charadriiformes_posteriors)
save(BMspace_charadriiformes_posteriors, file = "../Data/Processed/BMspace_charadriiformes_posteriors.MCMCglmm")
```

<!-- Figure 9: BMised shapespace mcmcmcglmmm diagnosis -->

@@

## Creating the dispRity objects

```{r, eval = TRUE, echo = FALSE}
## Get the shapespace
load(file = "../Data/Processed/params_shapespace_charadriiformes.rda")
shapespace <- param_chains$data
## Get the posteriors
load(file = "../Data/Processed/shapespace_charadriiformes_posteriors.MCMCglmm")

## Make the dispRity object
chara_shapespace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
                                     data          = shapespace,
                                     posteriors    = shapespace_charadriiformes_posteriors,
                                     group         = MCMCglmm.levels(shapespace_charadriiformes_posteriors)[1:4],
                                     rename.groups = c(levels(shapespace$level1), "phylogeny"))
covar.plot(chara_shapespace, ellipses = TRUE, major.axes = TRUE, n = 100, col = c("orange", "blue", "darkgreen", "grey"), legend = TRUE)
```

```{r, eval = TRUE, echo = FALSE}
## Get the shapespace
load(file = "../Data/Processed/params_ballspace_charadriiformes.rda")
shapespace <- param_chains$data
## Get the posteriors
load(file = "../Data/Processed/ballspace_charadriiformes_posteriors.MCMCglmm")

## Make the dispRity object
chara_ballspace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
                                    data          = shapespace,
                                    posteriors    = ballspace_charadriiformes_posteriors,
                                    group         = MCMCglmm.levels(ballspace_charadriiformes_posteriors)[1:4],
                                    rename.groups = c(levels(shapespace$level1), "phylogeny"))
covar.plot(chara_ballspace, ellipses = TRUE, major.axes = TRUE, n = 100, col = c("orange", "blue", "darkgreen", "grey"), legend = TRUE)
```

```{r, eval = TRUE, echo = FALSE}
## Get the shapespace
load(file = "../Data/Cluster/shapespace_charadriiformes/randospace_charadriiformes_1.mini.chains")
shapespace <- randospace_charadriiformes_$data
## Get the posteriors
load(file = "../Data/Processed/randospace_charadriiformes_posteriors.MCMCglmm")

## Make the dispRity object
chara_randospace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
                                     data          = shapespace,
                                     posteriors    = randospace_charadriiformes_posteriors,
                                     group         = MCMCglmm.levels(randospace_charadriiformes_posteriors)[1:4],
                                     rename.groups = c(levels(shapespace$level1), "phylogeny"))
covar.plot(chara_randospace, ellipses = TRUE, major.axes = TRUE, n = 100, col = c("orange", "blue", "darkgreen", "grey"), legend = TRUE)
```

```{r, eval = FALSE, echo = FALSE}
## Get the shapespace
load(file = "../Data/Cluster/shapespace_charadriiformes/BMspace_charadriiformes_1.mini.chains")
shapespace <- BMspace_charadriiformes_$data
## Get the posteriors
load(file = "../Data/Processed/BMspace_charadriiformes_posteriors.MCMCglmm")

## Make the dispRity object
chara_BMspace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
                                  data          = shapespace,
                                  posteriors    = BMspace_charadriiformes_posteriors,
                                  group         = MCMCglmm.levels(BMspace_charadriiformes_posteriors)[1:4],
                                  rename.groups = c(levels(shapespace$level1), "phylogeny"))
covar.plot(chara_BMspace, ellipses = TRUE, major.axes = TRUE, n = 100, col = c("orange", "blue", "darkgreen", "grey"), legend = TRUE)
```
